\begin{thebibliography}{XXXX}

\bibitem{verbr-cloud} Asadi, S., Nilashi, M., Husin, A.R.C. et al. -  Customers perspectives on adoption of cloud computing in banking sector. Inf Technol Manag 18, 305?330 (2017). [Online] Verfügbar unter: \url{https://doi.org/10.1007/s10799-016-0270-8} (Zugriff am: 23.01.2022)

\bibitem{def-cloud} Mell, Peter, and Tim Grance. - "The NIST definition of cloud computing." (2011). [Online] Verfügbar unter: \url{http://faculty.winthrop.edu/domanm/csci411/Handouts/NIST.pdf} (Zugriff am: 28.10.2021)

\bibitem{svc-mod} Chou, David. Cloud Service Models (IaaS, PaaS, SaaS) Diagram (2018). [Online] Verfügbar unter: \url{https://dachou.github.io/2018/09/28/cloud-service-models.html} (Zugriff am: 28.10.2021)

\bibitem{capex-opex} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.23.

\bibitem{total-cost} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.24.

\bibitem{econ-scale} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.24-25.

\bibitem{scale} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.27.

\bibitem{resil} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.26.

\bibitem{sec-1} Lisdorf, Anders. - Cloud computing basics a non-technical introduction. Berkeley, CA: Apress, 2021. S.25.

\bibitem{net-dep} NANDGAONKAR, Suruchee V.; RAUT, A. B. A comprehensive study on cloud computing. International Journal of Computer Science and Mobile Computing, 2014, 3. Jg., Nr. 4, S. 737.

\bibitem{sec-2} NANDGAONKAR, Suruchee V.; RAUT, A. B. A comprehensive study on cloud computing. International Journal of Computer Science and Mobile Computing, 2014, 3. Jg., Nr. 4, S. 737.

\bibitem{lock-in} OPARA-MARTINS, Justice; SAHANDI, Reza; TIAN, Feng. Critical analysis of vendor lock-in and its impact on cloud computing migration: a business perspective. Journal of Cloud Computing, 2016, 5. Jg., Nr. 1, S. 1-18. [Online] Verfügbar unter \url{https://ieeexplore.ieee.org/abstract/document/7009018} (Zugriff am: 24.01.2022)

\bibitem{migration-cost} BAI, Kun, et al. What to discover before migrating to the cloud. In: 2013 IFIP/IEEE International Symposium on Integrated Network Management (IM 2013). IEEE, 2013. S. 320. [Online] Verfügbar unter: \url{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=6573001} (Zugriff am: 24.01.2022)

\bibitem{csp-share} Kein Autor. Enterprise spending on cloud infrastructure services grows to USD 42 billion in Q2, 2021: SRG (2021) [Online] Verfügbar unter: \url{https://www.cioandleader.com/article/2021/07/30/enterprise-spending-cloud-infrastructure-services-grows-usd-42-billion-q2-2021} (Zugriff am: 24.01.2022)

\bibitem{gartner-mag} Bala, Raj; Gill, Bob; Smith, Dennis; Ji, Kevin; Wright, David. Magic Quadrant for Cloud Infrastructure and Platform Services (2021) [Online] Verfügbar unter: \url{https://www.gartner.com/doc/reprints?id=1-271OE4VR&ct=210802&st=sb} (Zugriff am: 24.01.2022)

\bibitem{def-iac} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.4

\bibitem{dec-imp-iac} Jacobs, Mike; Kaim, Ed. What is Infrastructure as Code? (2021) [Online] Verfügbar unter: \url{https://docs.microsoft.com/en-us/devops/deliver/what-is-infrastructure-as-code} (Zugriff am: 24.01.2022)

\bibitem{iac-schneller} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.3

\bibitem{conf-drift} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.17-18

\bibitem{cattle-pets} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.16

\bibitem{opt-change} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.4-5

\bibitem{stab-cloud} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.5

\bibitem{build-auto} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.6

\bibitem{speed-quality} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.8

\bibitem{coreprinc-1} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.10

\bibitem{coreprinc-2} Kief Morris. Infrastructure as Code. O?Reilly Media, 2. edition, 2020. S.11

\bibitem{iac-tools} Nayak, Ramnath. When to use which Infrastructure-as-code tool (2019) [Online] Verfügbar unter: \url{https://medium.com/cloudnativeinfra/when-to-use-which-infrastructure-as-code-tool-665af289fbde} (Zugriff am: 25.01.2022)

\bibitem{tf-princ} Terraform Website. [Online] Verfügbar unter: \url{https://www.terraform.io/} (Zugriff am: 25.01.2022)

\bibitem{hcl} Introduction to HashiCorp Configuration Language (HCL). [Online] Verfügbar unter: \url{https://www.linode.com/docs/guides/introduction-to-hcl/} (Zugriff am: 25.01.2022)

\bibitem{tf-provider} Terraform Language Documentation. [Online] Verfügbar unter: \url{https://www.terraform.io/language/providers} (Zugriff am: 26.01.2022)

\end{thebibliography}